\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Sean Duffy}
\address{ +44 7523 340034 \\ seanduffy@live.com  }

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

	\begin{rSection}{Experience}  
	    \begin{rSubsection}{Morgan Stanley}{Aug 2017 - Present}{Associate}{London}
	    \item Full-stack Java and C\# developer working on a high-volume multi-asset allocation system. Responsibilities include building new features and capabilities for users as well as ensuring the system meets regulatory demands.
	    \end{rSubsection}
	  
	    \begin{rSubsection}{Morgan Stanley}{June - Aug 2015, June - Aug 2016}{Summer Analyst}{London}
	    \item 2016: Spent ten weeks on a front-office team working on microservices to provide metadata to a sales and trading application. Technologies used include C\#, ASP.NET Web Api 2, Microsoft SQL Server.
	    \item 2015: Spent ten weeks working in the Application Support Group for FX. My main project was a web-based tool that allowed members of the support group to track the flow of orders and visualise order executions, allowing them to more easily diagnose problems. I used Python, Perl and KDB.
		\end{rSubsection}
		
	    \begin{rSubsection}{ScraperWiki}{Aug - Sept 2013, June - Sept 2014}{Software Engineering Intern}{Liverpool}
		\item 2014: Redesigned a component of ScraperWiki's cloud-based platform responsible for allowing users to export data in Microsoft Excel format. This was written in Go and made heavy use of concurrency. I also had to optimise the code to run in time and memory constraints and ensure scalability.
		\item 2013: I wrote web scraping tools for ScraperWiki's online platform, making use of Python and Regular Expressions as well as JavaScript, HTML and CSS for the frontend. I was also involved in work on the platform itself.
	    \end{rSubsection}
	\end{rSection}
    
	\begin{rSection}{Education}
	    {\bf University of York} \hfill {\em 2013 - 2017} \\ 
	    { Master of Engineering (MEng) in Computer Science } \\
	    { Upper second class (2:1) }
	    
	    {\bf Liverpool Blue Coat School } \hfill {\em 2011 - 2013} \\ 
	    \begin{tabular}{ @{} >{}l @{\hspace{6ex}} l }
	        A-Level Mathematics: & A \\
		    A-Level Computing: & A \\
			A-Level Physics: & B \\
			\end{tabular}
			
		{\bf Broadgreen International School } \hfill {\em 2006 - 2011 } \\ 
		{ 10 GCSEs A*-C } 
  	\end{rSection}
  
	\begin{rSection}{Technical Skills \& Expertise }
		I have over two years of industry experience building applications with Java servers and C\# WPF GUIs. I am also familiar with Python, Go, JavaScript, JQuery, HTML and CSS. I have used Git and Perforce for version control and have experience with agile software development,  test driven development and continuous integration.
	\end{rSection}
	
	\vspace*{\fill}
 	{ References are available on request. }


\end{document}