\documentclass{resume}

\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.6in]{geometry}

\name{Sean Duffy}
\address{ +44 7523 340034 \\ seanduffy@live.com  }

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}
  
  \begin{rSection}{Experience}
  
    \begin{rSubsection}{Morgan Stanley}{August 2017 - Present}{Associate}{London}
    \item Full-stack Java and C\# developer working on a high-volume multi-asset allocation system. Responsibilities include building new features and capabilities for users as well as ensuring the system meets regulatory demands.
    \end{rSubsection}
  
    \begin{rSubsection}{Morgan Stanley}{June - August 2015, June - August 2016}{Summer Analyst}{London}
    \item 2016: Spent ten weeks on a front-office team working on microservices to provide metadata to a sales and trading application. Technologies used include C\#, ASP.NET Web Api 2, Microsoft SQL Server.
    \item 2015: Spent ten weeks working in the Application Support Group for FX. My main project was a web-based tool that allowed members of the support group to track the flow of orders and visualise order executions, allowing them to more easily diagnose problems.
    
    \end{rSubsection}

    \begin{rSubsection}{ScraperWiki}{June - September 2014}{Software Engineering Intern}{Liverpool}
	\item Redesigned a component of ScraperWiki's cloud-based platform responsible for allowing users to export data in Microsoft Excel format. This was written in Go and made heavy use of concurrency. I also had to optimise the code to run in time and memory constraints and ensure scalability.
    \end{rSubsection}
  
  \end{rSection}
  
    \begin{rSection}{Education}
    
    {\bf University of York} \hfill {\em 2013 - 2017} \\ 
    { Master of Engineering (MEng) in Computer Science } \\
    { Upper second class (2:1) }
    
    {\bf Liverpool Blue Coat School } \hfill {\em 2011 - 2013} \\ 
    \begin{tabular}{ @{} >{}l @{\hspace{6ex}} l }
        A-Level Mathematics: & A \\
	    A-Level Computing: & A \\
		A-Level Physics: & B \\
		\end{tabular}
		
	{\bf Broadgreen International School } \hfill {\em 2006 - 2011 } \\ 
	{ 10 GCSEs A*-C } 
    
  	\end{rSection}
  
	\begin{rSection}{Technical Skills \& Expertise }

    
	{ References available on request. }
    
	\end{rSection}
  

\end{document}